Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-05 apples_and_oranges.qmd
lots of new code

###########3. Function to extract parameters (coefs, ses, CI) for each level of the dummy #variable
# it is a slightly awkward one, because I couldnt' come up with a better way to add the intercept to #each coefficient
# given the named output of the built in coef function. 
# here I exctract the coeffcients
extract_coefficients_func <- function(df_with_coefs){
  list_coefs <- list()
  coefs <- 0
  coefficient_output <- 0

@@

############4. Function to get the means out of the extracted parameters
# here the argument list_of_dfs is the list of extracted coefficients that you get out of the #extract_coefficients_func
# which itself you get from the run_metaregression function. The argument conditions refers to #the levels of the variable that describes each study arm

@@

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
library(tidyverse)

# describe studies
n_unique_studies <- length(unique(df_long_for_metan$new_study_id))

df_count_studies <- df_long_for_metan %>% 
  group_by(psy_or_med, arm_effect_size) %>% 
  count(is.na(cohens_d))

df_count_studies <-rename(df_count_studies, is_missing = `is.na(cohens_d)`)

df_count_studies <-
  df_count_studies %>% 
  mutate(condition = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
                             psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
                             psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
                             psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
  )

df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
```

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Run metaregression ------------------------------------------------------
library(metafor)
# add a new multilevel variable for the regression

@@

# A. Estimate Means and CIs for the overall ----------------------------------
# specify model
model_1 <- as.formula(~ four_level_var)

@@

# extract coefs from the  list
list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)

# calculate mean coefs and ses
df_mean_coefs_from_sim <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, conditions)

@@

# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
# first grab ids for those studies
cbt_fluox_esc_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

@@

model_1 <- as.formula(~ four_level_var)

# apply the metareg function to the list of cbt, fluox, esc
list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)

# extract coefs from the list for cbt fluox escit
means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)

# calculate mean coefs and ses
conditions <- unique(list_df_simulated[[1]]$four_level_var) # for the conditino argument
coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, conditions)
 coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))

@@

@@

# apply the function to the list of cbt, fluox, esc
list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)

@@

# run the mean function for no wl
conditions <- unique(list_df_simulated[[1]]$four_level_var) # for the conditino argument
coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, conditions)
coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))

 #add the ns of studies FIX THIS

 df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))

@@

```
We examined the variability that the simulations of the correlations of the pre-post outcomes produced. As shown in Supplemenatry Table 2, the standard deviation of the simulated mean varied in the third decimal point, indicating minimal influence of the correlations on the outcomes.

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# plot results from simulated means ---------------------------------------

# Create summary stats text
df_mean_coefs_from_sim$text_label <- 0
for(i in 1: nrow(df_mean_coefs_from_sim))
df_mean_coefs_from_sim$text_label[i] <-  paste(
   "k = ", df_mean_coefs_from_sim$n[i],"\n", 
   round(df_mean_coefs_from_sim$coef_means[i], 2),
   "[" ,
 round(df_mean_coefs_from_sim$lower_ci[i],2), 
 round(df_mean_coefs_from_sim$upper_ci[i], 2),
"]")

# recode condition for ease of plotting
df_mean_coefs_from_sim$condition <- str_replace_all(df_mean_coefs_from_sim$condition, "_", " ")

# encode colours
redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")

plot_means <- ggplot(df_mean_coefs_from_sim, aes(x = coef_means, y = 1:nrow(df_mean_coefs_from_sim),
                                   colour = condition, label = text_label)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
  geom_text(vjust = +1.5, size = 4) +  # Adjust vjust and size as needed
  scale_size_continuous(guide = "none") +
  guides(colour = FALSE) + 
  scale_color_manual(values = c(redish_palette, blueish_palette)) +
  theme_minimal() +
  labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
       subtitle = "metanalytically derived estimates of within group changes") +
  xlab("Standardized Mean Difference (SMD) with 95% CIs") +
  ylab("") +
  ylim(0, nrow(df_mean_coefs_from_sim) + 1) +
  xlim(-2.5, 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
  geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
  geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
  theme(axis.title.x = element_text(size = 14), 
        axis.text.x  = element_text(size = 14),
        axis.text.y = (element_blank()),
        plot.title = element_text(size = 16),
        plot.subtitle = element_text(size = 14))+
  geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
  geom_text(x = 0.2, y = 4.75, label = "Line of No Effect", color = "grey", vjust = 0.5, hjust = 0)

png("plotted_means.png")
plot_means
dev.off()

![Fig 1. Means of the Four Trial Arms](plotted_means.png){width=50%}

```{r, warning=FALSE, message = FALSE, echo=FALSE}
coefs<- 0
ses <- 0
for(i in 1: length(list_model_1_meta_reg)){

  coefs[[i]] <- coef(list_model_1_meta_reg[[i]])[[4]]  ### CAREFUL this is poor coding practice on my part
  ses[[i]] <- list_model_1_meta_reg[[i]]$se[4] ### but I can't find another way of grabbing this estimate from the
  ### rma object. It could go badly wrong if the relevelling isn't done consistently...CHECK MANUALLY
  coefficients_from_contrasts_medcontrol_psy_control <- data.frame(Beta = mean(coefs), SE = mean(ses))
}

coefficients_from_contrasts_medcontrol_psy_control$lower_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta - 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE

coefficients_from_contrasts_medcontrol_psy_control$upper_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta + 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE

coefficients_from_contrasts_medcontrol_psy_control$zed_value <- coefficients_from_contrasts_medcontrol_psy_control$Beta/
coefficients_from_contrasts_medcontrol_psy_control$SE

coefficients_from_contrasts_medcontrol_psy_control$p_value <- format(1 - pnorm(coefficients_from_contrasts_medcontrol_psy_control$zed_value), scientific = TRUE)

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
#| label: Table 2
#| tbl-cap: Statistics of the Difference Between Medication and Psychotherapy Control Conditions
knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control,col.names = c("Beta", "SE", "Lower CI", "Upper CI", "z-value", "p-value"), digits = 2)

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# filter dataset to include only those ids with cbt fluox or escitalopram

# grab those ids
cbt_fluox_esc_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

# subset all dataframes in the list
list_cbt_fluox_esc_study <- list()

# apply the function to the list of cbt, fluox, esc
list_model_1_meta_reg_cbt_fluox_esc <- run_metaregression(list_cbt_fluox_esc_study, model_1)

# now use the function to extract the coefficients

list_model_1_meta_reg_cbt_fluox_esc[[1]]
```

>>>>

#########2. Function to count studies with missingness etc.

count_studies <- function(df) {
  df_count_studies <- df %>%
    group_by(psy_or_med, arm_effect_size) %>%
    count(is.na(cohens_d)) %>%
    rename(is_missing = `is.na(cohens_d)`) %>%
    mutate(
      condition = case_when(
        psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
        psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
        psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
        psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control"
      )
    )

  return(df_count_studies)
}

##########3. Function to extract mean coefficients and to extract model characteristics

aggregate_model_results <- function(list_model_1_meta_reg, condition) {
  df_coefs <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
  df_se <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
  df_z_value <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
  df_lower_ci <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
  df_upper_ci <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
  tau_sq <- rep(0, length(list_model_1_meta_reg))
  i_sq <- rep(0, length(list_model_1_meta_reg))
  k <- rep(0, length(list_model_1_meta_reg))
  r_sq <- rep(0, length(list_model_1_meta_reg))

  for (i in 1:length(list_model_1_meta_reg)) {
    for (j in 1:length(condition)) {
      df_coefs[i, j] <- list_model_1_meta_reg[[i]]$beta[[j]]
      df_se[i, j] <- list_model_1_meta_reg[[i]]$se[[j]]
      df_z_value[i, j] <- list_model_1_meta_reg[[i]]$zval[[j]]
      df_lower_ci[i, j] <- list_model_1_meta_reg[[i]]$ci.lb[[j]]
      df_upper_ci[i, j] <- list_model_1_meta_reg[[i]]$ci.ub[[j]]
      tau_sq[i] <- list_model_1_meta_reg[[i]]$tau2
      i_sq[i] <- list_model_1_meta_reg[[i]]$I2
      k[i] <- list_model_1_meta_reg[[i]]$k
      r_sq[i] <- list_model_1_meta_reg[[i]]$R2
    }
  }

  df_coefficients_model <- data.frame(
    coefficients = colMeans(df_coefs),
    se = colMeans(df_se),
    z_value = colMeans(df_z_value),
    lower_ci = colMeans(df_lower_ci),
    upper_ci = colMeans(df_upper_ci),
    tau_sq = mean(tau_sq),
    i_sq = mean(i_sq),
    k = mean(k),
    r_sq = mean(r_sq)
  )

  return(df_coefficients_model)
}

###########4. Function to extract the SMDs  (SMD, ses, CI) for each level of the dummy #variable. The output is used below in 5.
# it is a slightly awkward one, because I couldnt' come up with a better way to add the intercept to #each coefficient
# given the named output of the built in coef function. 
# here I exctract the coeffcients
extract_coefficients_func <- function(df_with_coefs){
  list_coefs <- list()
  coefs <- 0
  coefficient_output <- 0

@@

############5. Function to get the means out of the SMDs (this is similar to Func 3 and I should at some point create one more general one)
# here the argument list_of_dfs is the list of extracted coefficients that you get out of the #extract_coefficients_func
# which itself you get from the run_metaregression function. The argument conditions refers to #the levels of the variable that describes each study arm

@@

###############6. Function for plotting the SMDs
library(ggplot2)
library(stringr)

plot_means_function <- function(dataframe, subtitle) {
  dataframe$text_label <- 0

  for (i in 1:nrow(dataframe)) {
    dataframe$text_label[i] <- paste(
      "k = ", dataframe$n[i], "\n",
      round(dataframe$coef_means[i], 2),
      "[" ,
      round(dataframe$lower_ci[i], 2), 
      round(dataframe$upper_ci[i], 2),
      "]"
    ) 
  }

  # Recode condition for ease of plotting
  dataframe$condition <- str_replace_all(dataframe$condition, "_", " ")

  # Encode colours
  redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
  blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")

  # Plotting
  plot_means <- ggplot(dataframe, aes(x = coef_means, y = 1:nrow(dataframe),
                                      colour = condition, label = text_label)) +
    geom_point(size = 3) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
    geom_text(vjust = +1.5, size = 4) +
    scale_size_continuous(guide = "none") +
    guides(colour = FALSE) + 
    scale_color_manual(values = c(redish_palette, blueish_palette)) +
    theme_minimal() +
    labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
         subtitle = subtitle) +
    xlab("Standardized Mean Difference (SMD) with 95% CIs") +
    ylab("") +
    ylim(0, nrow(dataframe) + 1) +
    xlim(-3.0, 0.5) +
    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
    theme(axis.title.x = element_text(size = 14), 
          axis.text.x  = element_text(size = 14),
          axis.text.y = (element_blank()),
          plot.title = element_text(size = 16),
          plot.subtitle = element_text(size = 14)) +
    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey", vjust = 0.5, hjust = 0)

  return(plot_means)
}

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# library(tidyverse)
# 
# 
# # describe studies
# n_unique_studies <- length(unique(df_long_for_metan$new_study_id))
# 
#   
# 
# df_count_studies <- df_long_for_metan %>% 
#   group_by(psy_or_med, arm_effect_size) %>% 
#   count(is.na(cohens_d))
# 
# 
# df_count_studies <-rename(df_count_studies, is_missing = `is.na(cohens_d)`)
# 
# df_count_studies <-
#   df_count_studies %>% 
#   mutate(condition = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
#                              psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
#                              psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
#                              psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
#   )
# 
#   df_count_studies$condition <- factor(df_count_studies$condition) # turn to factor
#   
#   # relevel so that medication control becomes the reference category for the regression
#   df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
# 
# df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
```

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Get Ns, run metareg, prepare graphing ------------------------------------------------------
library(tidyverse)
library(metafor)

# add a new multilevel variable for the regression

@@

# A. Estimate Means and CIs for the overall ----------------------------------

# count studies
# count the number of studies
n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check

# specify model
model_1 <- as.formula(~ four_level_var)

@@

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)

# extract SMDs from the  list
list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)

# calculate mean SMDs and ses
df_mean_coefs_from_sim <- calculate_mean_coefs_ses(list_dummy_var_means, condition)

@@

# add the ns
df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))

# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
#  grab ids for those studies
cbt_fluox_esc_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id

@@

# count the number of studies
study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
# CHARLOTTE please check

# apply the metareg function to the list of cbt, fluox, esc
model_1 <- as.formula(~ four_level_var)
list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)

# extract SMDs from the list for cbt fluox escit
means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)

# calculate mean SMDs and ses
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
 coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))

# add the ns to the dataframe
 coef_and_se_means_cbt_fluox_esc_study$n  <- study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing ==F,]$n

@@

# count studies 
study_count_no_wl_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_ids,])
# CHARLOTTE please check

@@

# apply the metareg function to the list of cbt, fluox, esc
list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)

@@

# run the mean function for no wl
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, condition)
coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))

coef_and_se_means_no_wl$n <- study_count_no_wl_study[study_count_no_wl_study$is_missing 
                                                     ==FALSE,]$n

@@

NOTE: CHARLOTTE Please create a table here with the results from the count studies or study count variables that you checked in the code chunk above for each A,B and C. 
The table for A should be added here and accompany the description below. 
THe other two should go below as supplementary.
As indicated in the methods we should have one overall table with all studies and all their characteristics ala Cipriani.

We examined the variability that the simulations of the correlations of the pre-post outcomes produced. As shown in Supplemenatry Table 2, the standard deviation of the simulated mean varied in the third decimal point, indicating minimal influence of the correlations on the outcomes.

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# plot results from simulated means ---------------------------------------
# 
subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
print(plot_means_all)

subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
print(plot_means_cbt)

subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
print(plot_means_wl)

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# #| label: Table 2
# #| tbl-cap: Statistics of the Difference Between Medication and Psychotherapy Control Conditions
# knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control,col.names = c("Beta", "SE", "Lower CI", "Upper CI", "z-value", "p-value"), digits = 2)

@@

```{r}
# examine the stability of the simulations
stability_sims %>%
  ggplot(aes(x = n_sims, y = z_value)) +
  geom_point() +
  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
               arrow = arrow(length = unit(0.3, "cm")),
               color = "black") +
  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line are statistically significant)", hjust = -0.1, vjust = 0) +
  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
               arrow = arrow(length = unit(0.3, "cm")),
               color = "black") +
  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
           hjust = -0.1, vjust = 0) +
  theme_minimal() +
  labs(
    x = "Number of Simulations",
    y = "z-value",
    title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
    subtitle = "Results from 1000 simulations with within-group standard errors"
  )
